

\subsection*{Weekely meetings}
\label{sec:meetings}


This section contains the results of the weekly meetings are communicated
via email to the group members. There are kept here for quick reference.


\begin{center}
  \begin{tabular}[t]{r@{\quad}l@{\quad\quad}p{9cm}}
    0.
    &
    9. April
    &
    no meeting this week, only email
    \\
    1.
    &
    \url{meetings/meeting-160402.txt}{16. April}
    &
    task assignment, change of meeting time
    \\
    2.
    & 
    \url{meetings/meeting-240402.txt}{24. April}
    &
    no real decisions
    \\
    3.
    &
    1.\ May
    &
    holyday
    \\
    4.
    \url{meetings/meeting-080502.txt}{8.\ May}
    & 
    task presentation
    \\
  \end{tabular}
\end{center}



Organisatorial/procedural things discussed during the meeting at 3.7.02
included arguments mentioned \url{slides/meeting030702.ps}{here.}


Here the \important{official decision} concerning the \texttt{CLASSPATH}
etc. (same is in \texttt{Readme.devel}).

\begin{itemize}
\item the \importantxx{checked-in} versions of cup and lex are
  obligatory\footnote{They replace the ones previously used under
    \texttt{/home/java}, which had been the official ones so far. In
    effect, they are the same, and just checked in.}
\item the following \importantxx{classpath} is obligatory:
  \texttt{CLASSPATH=<WORKDIR>/Slime/src:<WORKDIR>/Slime/lib/JLex.jar:<WORKDIR>/Slime/lib/java_cup.jar:}
  where of course the \texttt{<WORKDIR>} is a placeholder and it has to be
  adapted by the individual user to his work directory.
\item no \importantxx{generated} files nor \importantxx{class} files will be
  checked in (unless technical reasons call for it, in which case we will
  discuss this in the light of the new arguments again)
\item no \importantxx{non-slime} code or data will be checked in under
  \texttt{CLASSPATH=<WORKDIR>/Slime/src}
\item revisions \emph{log}s are useful and worth reading, but it's not
  mandatory to read each other's logs.
\end{itemize}



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "meetings"
%%% End: 
